Red-Giant Hot Jupiters: Brilliant Radio Beacons?

### 2015-06-01 ms.tex
Explanation for the magnetic case is added

In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$.

Magnetic field of evolved stars are not well constrained \citep{konstantinova2010}. 
If the correlation with input magnetic energy is the case, the radio emission would be rather weaker than the Jupiter, because the magnetic field of evolved stars

>>>>

In this paper, we assume that the radio emission is scaled with the input kinetic energy, i.e., $P_{\rm radio} \propto P_{\rm k,\,inp}$, because as indicated earlier, the kinetic energy of the stellar wind of evolved stars are much larger than the main-sequence stars and thus may lead to brighter radio emission. 
On the other hand, if the correlation with input magnetic energy is more fundamental, it is difficult to estimate the planetary radio emission at this point because magnetic field of evolved stars have not be well constrained for most of the highly evolved stars. 
Recently there are some observations for M giants, which measured surface magnetic field $\sim 0.1-10 $G for a M-type star EK Boo  \citep{konstantinova2010}. In this particular case, given the large stellar radius $R_\star \sim 210 R_{\odot }$ the magnetic moment may be about $10^3$ times larger than the Sun and thus also may also increase the planetary radio emission. However, because of the lack of universal understanding of the stellar magnetic field, we leave the magnetic model of radio emission for evolved stars for future work.

the radio emission could be rather weaker than the Jupiter, 
We note that, if the correlation with input magnetic energy is the case, the radio emission could be rather weaker than the Jupiter, because the magnetic field of evolved stars
